---
title: "05_analyses_05_emo_score"
author: "Sebastian Sauer"
date: "15 9 2017"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

opts_knit$set(root.dir = normalizePath('../')) # knitrs takes the folder of the Rmd-file as root.dir, but RStudio in interactive mode takes the project folder as root. Better to align both.

```


# Setup


First load some libraries.

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(magrittr)
library(tidytext)
library(stringr)
library(viridis)
library(wordcloud)
library(SnowballC)
library(knitr)
```


And the data.
```{r load-data}
load("../data_polit_twitter/tweets_df.Rdata")
load("../data_polit_twitter/tweet_tokens.Rdata")
load("../data_polit_twitter/polits_df.Rdata")
load("data/party_pal.Rdata")
load("../data_polit_twitter/party_pop_scores.Rdata")
horde <- read_csv("data/hordenlexikon.csv")
load("../data_polit_twitter/tweet_tokens_sentis.Rdata")


```

# Plot emo score - Top 25 politicians

```{r p_top_emo_scores}
polits_df %>% 
  select(screenName, party, emo_abs_score_z) %>% 
  arrange(-emo_abs_score_z) %>% 
  slice(1:25) %>% 
  ggplot() +
  aes(x = reorder(screenName, emo_abs_score_z), 
      y = emo_abs_score_z) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Emotionsgehalt (z-Wert)",
       title = "Die Politiker mit den emotionalsten Tweets:\nbunte Vielfalt der Parteien") -> p_emo_top_25 

p_emo_top_25
ggsave(p_emo_top_25, file = "img/p_emo_top_25.pdf",
       width = 8,
       height = 6)

```



# Plot emo score - per party

```{r p_emo_per_party}
polits_df %>% 
  select(screenName, party, emo_abs_score_z) %>% 
  group_by(party) %>% 
  filter(!(party %in% c("trump", "fraktionslos"))) %>% 
  summarise(emo_abs_score_z = median(emo_abs_score_z, na.rm = T)) %>% 
  ggplot() +
  aes(x = reorder(party, emo_abs_score_z), 
      y = emo_abs_score_z) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Partei",
       fill = "Partei",
       y = "Emotionsgehalt (Median über z-Werte der Politiker)",
       title = "Die Parteien mit den emotionalsten Tweets:\nAfD führt, gefolgt von der Linken. Die CSU ist am nüchternsten") -> p_emo_per_party

p_emo_per_party
ggsave(p_emo_per_party, file = "img/p_emo_per_party.pdf",
       width = 8,
       height = 6)
ggsave(p_emo_per_party, file = "img/p_emo_per_party.png",
       width = 8,
       height = 6)

```



# Plot frequency of emotional words - per party

```{r p_emo_words_per_party}
polits_df %>% 
  select(screenName, party, emo_words_prop_z) %>% 
  group_by(party) %>% 
  filter(!(party %in% c("trump", "fraktionslos"))) %>% 
  summarise(emo_words_prop_z = median(emo_words_prop_z, na.rm = T)) %>% 
  ggplot() +
  aes(x = reorder(party, emo_words_prop_z), 
      y = emo_words_prop_z) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Partei",
       fill = "Partei",
       y = "Anteil emotionaler Wörter (Median über z-Werte der Politiker)",
       title = "Emotionsgehalt der Tweets nach Parteien",
       caption = "Die FDP verwendet im Vergleich sehr viele emotionale Wörter,\ndie Linke am wenigsten")  -> p_emo_words_per_party

p_emo_words_per_party
ggsave(p_emo_words_per_party, file = "img/p_emo_words_per_party.pdf",
       height = 6,
       width = 8)

```




# Plot intensity of emotional words - top 100


```{r top_100_emo_tokens}
tweet_tokens_sentis %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  arrange(-Wert_abs) %>% 
  select(token, Wert_abs) %>% 
  distinct %>% 
  slice(1:100) %>% 
  pull(token) -> top_100_emo_tokens
  
```


```{r p_most_emo_words}

tweet_tokens_sentis %>% 
  select(screenName, token, Wert, party) %>% 
  filter(party != "trump") %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  filter(token %in% top_100_emo_tokens) %>% 
  ggplot +
  aes(x = reorder(token, Wert_abs), y = Wert_abs, color = party) +
  geom_jitter(width = .3, height = .3) +
  coord_flip() +
  scale_color_manual(values = party_pal) +
  labs(x = "Wort",
       y = "Emotionaler Wert",
       color = "Partei",
       title = "Die 1% emotionalsten Wörter in den Tweets: gelb dominiert") -> p_most_emo_words


p_most_emo_words
ggsave(p_most_emo_words, file = "img/p_most_emo_words.pdf",
       width = 11,
       height = 8)

```



```{r p_most_emo_words_facets}
tweet_tokens_sentis %>% 
  select(screenName, token, Wert, party) %>% 
  filter(party != "trump") %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  group_by(party) %>% 
  arrange(-Wert_abs, .by_group = TRUE) %>% 
  mutate(rank_ = percent_rank(Wert_abs)) %>% 
  filter(rank_ > .99) %>%  
  ungroup %>%  
  ggplot +
  aes(x = reorder(token, Wert_abs), y = Wert_abs, color = party) +
  geom_jitter(width = .15, height = .15) +
  facet_wrap(~party, scales = "free") +
  coord_flip() +
  scale_y_continuous(breaks = c(0.8, 0.9, 1)) +
  scale_color_manual(values = party_pal) +
  labs(x = "Wort",
       y = "Emotionaler Wert",
       color = "Partei",
       caption = "Die emotional intensiven Wörter werden von allen Parteien ähnlich verwendet",
       title = "Die 1% emotionalsten Wörter in den Tweets (pro Partei)") -> p_most_emo_words_facets


p_most_emo_words_facets
ggsave(p_most_emo_words_facets, file = "img/p_most_emo_words_facets.pdf",
       width = 15,
       height = 10)
ggsave(p_most_emo_words_facets, file = "img/p_most_emo_words_facets.png",
       width = 15,
       height = 10)
```


# Proportion of parties in the 100 most emotional tokens
In the 100 most emotional tokens, which party has which share?


```{r}
tweet_tokens_sentis %>% 
  filter(token %in% top_100_emo_tokens) %>% 
  filter(party != "trump") %>% 
  select(screenName, party, token, Wert) %>% 
  count(party) %>% 
  arrange(n) %>% 
  ggplot +
  aes(x = reorder(party, n), y = n, fill = party) +
  geom_col() +
  scale_fill_manual(values = party_pal) +
  coord_flip() +
  labs(x = "Partei",
       y = "Anteil an den emotionalsten Wörtern",
       fill = "Partei")
```



# Emotional intensive of tokens in tweets per party

```{r}
tweet_tokens_sentis %>% 
  select(screenName, token, Wert, party) %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  filter(party != "trump") %>% 
  group_by(party) %>% 
  summarise(Emo_abs_md = mean(Wert_abs),
            n = n()) %>% 
  ggplot +
  aes(x = reorder(party, Emo_abs_md), y = Emo_abs_md, color = party) +
  geom_point() +
  coord_flip() +
  scale_color_manual(values = party_pal)
```


# Difference in most emotional tweets between parties


```{r top_100_emo_words_afd}
tweet_tokens_sentis %>% 
  select(screenName, token, Wert, party) %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  filter(party == "afd") %>% 
  arrange(-Wert_abs) %>% 
  select(token) %>% 
  distinct %>% 
  slice(1:100) %>% 
  pull(token) -> top_100_emo_words_afd
```



```{r top_100_emo_words_nonafd}
tweet_tokens_sentis %>% 
  select(screenName, token, Wert, party) %>% 
  mutate(Wert_abs = abs(Wert)) %>% 
  filter(party != "afd") %>% 
  arrange(-Wert_abs) %>% 
  select(token) %>% 
  distinct %>% 
  slice(1:100) %>% 
  pull(token) -> top_100_emo_words_nonafd
```


Words in top list of the AfD but not in the rest of the Parties

```{r}
setdiff(top_100_emo_words_afd, top_100_emo_words_nonafd) -> afd_unique_top_words

save(afd_unique_top_words, file = "../data_polit_twitter/afd_unique_top_words.Rdata")


```

Words that appeared in the top list of the AfD AND as well in the top list of the rest of the parties.

```{r}
  intersect(top_100_emo_words_afd, top_100_emo_words_nonafd) -> common_words_afd_rest_top_words


save(common_words_afd_rest_top_words, file = "../data_polit_twitter/common_words_afd_rest_top_words.Rdata")
```


# Correlation of deutsch-score and emo-score

```{r p_emo_deutsch}

polits_df %>% 
  ggplot +
  aes(x = deutsch_score_z, 
      y = emo_abs_score_z, 
      color = party) +
  geom_point() +
  scale_color_manual(values = party_pal) +
  labs(x = "Deutsch-Score",
       y = "Emo-Score",
       color = "Partei",
       title = "Zusammenhang von Deutsch-Score und Emo-Score",
       caption = "Kein Zusammenhang ersichtlich") -> p_emo_deutsch

ggsave(p_emo_deutsch, file =
         "img/p_emo_deutsch.png",
       width = 9,
       height = 5)

```



```{r p_emo_deutsch_afd_only}

polits_df %>% 
  filter(party == "afd") %>% 
  ggplot +
  aes(x = deutsch_score_z, 
      y = emo_abs_score_z, 
      color = party) +
  geom_point() +
  scale_color_manual(values = party_pal) +
  labs(x = "Deutsch-Score",
       y = "Emo-Score",
       color = "Partei",
       title = "Zusammenhang von Deutsch-Score und Emo-Score",
       caption = "Je emotionaler, desto weniger 'deutsch*'") + 
  geom_smooth(method = "lm", color = "grey20", se = F) -> p_emo_deutsch_afd_only

p_emo_deutsch_afd_only

ggsave(p_emo_deutsch_afd_only, file =
         "img/p_emo_deutsch_afd_only.png",
       width = 8,
       height = 6)

```
