---
title: "Computing the Urhorde-Score"
author: "Sebastian Sauer"
date: "3 8 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath('../'))


knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.align = "center",
                      cache = TRUE)
```


---

 Work in progress. DRAFT.

---


Let's perform some  analyses of polit tweets.

# Setup


First load some libraries.

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(magrittr)
library(tidytext)
library(stringr)
library(viridis)
library(wordcloud)
library(SnowballC)
library(knitr)
```


And the data.
```{r load-data}
load("../data_polit_twitter/tweets_df.Rdata")
load("../data_polit_twitter/tweet_tokens.Rdata")
load("../data_polit_twitter/polits_df.Rdata")
load("data/party_pal.Rdata")
load("../data_polit_twitter/party_pop_scores.Rdata")
horde <- read_csv("data/hordenlexikon.csv")


```


glimpse

```{r}
glimpse(horde)

horde
```


# Count horde tokens

## Join token_df with horde


```{r}
tweet_tokens %>% 
  inner_join(horde, by = "token") -> horde_tokens
```



## Count per account and join with polits_df


```{r}
horde_tokens %>% 
  group_by(screenName) %>% 
  summarise(n_horde = n()) -> horde_accounts


if ("n_horde" %in% names(polits_df)){
  cat("'n_horde' is already a column in 'polits_df'. Do not join again.")
} else {
polits_df %>% 
  left_join(horde_accounts, by = "screenName") -> polits_df
  cat("Column'n_horde' was joined to 'polits_df'.\n")}
```


## Compute relative horde measure

```{r}
polits_df %>% 
  mutate(horde_score = (n_horde / n) * 100) -> polits_df

```


## Count the token "deutsch" in tweet_tokens


```{r}
tweet_tokens %>% 
  filter(str_detect(token, "deut\\w+")) %>% 
  count(screenName, sort = TRUE) %>% 
  rename(n_deutsch = n) -> deutsch_screenName
  

```


## Join with polits_df

```{r}

if ("n_deutsch" %in% names(polits_df)){
  cat("Column 'n_deutsch' is already present in 'polits_df'. Abort Joining.")
} else {
polits_df %>% 
  left_join(deutsch_screenName) %>% 
  mutate(deutsch_score = n_deutsch / n) -> polits_df 
  cat("Column 'n_deutsch' was joined to polits_df\n") }

if ("Deutsch_score" in names(polits_df)){
  polits_df %>% 
  rename(deutsch_score = Deutsch_score) -> polits_df}
```

# No more data manipulation below this line!

(In this file)


# Save data

```{r}
save(polits_df, file = "../data_polit_twitter/polits_df.Rdata")

```


## Plot Horden-Score

```{r}

polits_df %>% 
  select(screenName, party, horde_score) %>% 
  arrange(-horde_score) %>% 
  slice(1:25) %>% 
  ggplot() +
  aes(x = reorder(screenName, horde_score), y = horde_score) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Relative Häufigkeit von Hordenwörtern") -> p_horde_01

p_horde_01

ggsave(p_horde_01, file = "img/p_horde_01.png",
       width = 7,
       height = 4)
```




## Plot Deutsch-Scores

```{r}
polits_df %>% 
  select(screenName, party, deutsch_score) %>% 
  arrange(-deutsch_score) %>% 
  slice(1:25) %>% 
  ggplot() +
  aes(x = reorder(screenName, deutsch_score), 
      y = deutsch_score) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Relative Häufigkeit von 'Deutsch'") -> p_horde_02

p_horde_02

ggsave(p_horde_02, file = "img/p_horde_02.png",
       width = 7,
       height = 4)
```

## Plot deutsch score per party

```{r p_horde_03_geom_col}
polits_df %>% 
  select(screenName, party, deutsch_score) %>% 
  filter(party != "trump") %>% 
  group_by(party) %>% 
  summarise(deutsch_score_party = median(deutsch_score, na.rm = T)) %>% 
  ggplot() +
  aes(x = reorder(party, deutsch_score_party), 
      y = deutsch_score_party) +
  geom_col(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Relative Häufigkeit von 'Deutsch'") -> p_horde_03

p_horde_03

ggsave(p_horde_03, file = "img/p_horde_03.png",
       width = 7,
       height = 4)
```


```{r p_horde_03_geom_col_deutsch_boxplot}
polits_df %>% 
  select(screenName, party, deutsch_score) %>% 
  group_by(party) %>% 
  mutate(deutsch_score_party = median(deutsch_score, na.rm = T)) %>% 
  ungroup %>% 
  filter(party != "trump") %>% 
  ggplot() +
  aes(x = reorder(party, deutsch_score_party), 
      y = deutsch_score) +
  geom_boxplot(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Relative Häufigkeit von 'Deutsch'") -> p_horde_03_boxplot_deutsch

p_horde_03_boxplot_deutsch

ggsave(p_horde_03_boxplot_deutsch, file = "img/p_horde_03_boxplot_deutsch.png",
       width = 7,
       height = 4)
ggsave(p_horde_03_boxplot, file = "img/p_horde_03_boxplot_deutsch.pdf")
```


## Plot horden scores per party

```{r}
polits_df %>% 
  select(screenName, party, horde_score) %>% 
  group_by(party) %>% 
  mutate(horde_score_party = median(horde_score, na.rm = T)) %>% 
  ungroup %>% 
  filter(party != "trump") %>% 
  ggplot() +
  aes(x = reorder(party, horde_score_party), 
      y = horde_score) +
  geom_boxplot(aes(fill = party)) +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Politiker",
       fill = "Partei",
       y = "Relative Häufigkeit von Horden-Wörtern") -> p_horde_04_boxplot

p_horde_04_boxplot

ggsave(p_horde_04_boxplot, file = "img/p_horde_04_boxplot.png",
       width = 7,
       height = 4,
       dpi = 800)

ggsave(p_horde_04_boxplot, file = "img/p_horde_04_boxplot.pdf")

```



# Correlation of Horde score, populism score, and deutsch score


```{r}
library(GGally)
polits_df %>% 
  select(screenName, party, horde_score, deutsch_score, pop_z_md) %>% 
  filter(party != "trump") %>% 
  rename(Name = screenName,
         Partei = party,
         Horden_Score = horde_score,
         Deutsch_Score = deutsch_score,
         Populismus_Score = pop_z_md) %>% 
  ggpairs(data = .,
          columns = 3:5)
```

No real association, it appears.
