---
title: "Computing a populism measure"
author: "Sebastian Sauer"
date: "3 8 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath('../'))


knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.align = "center",
                      cache = TRUE)
```


---

 Work in progress. DRAFT.

---


Let's perform some  analyses of polit tweets.

# Setup


First load some libraries.

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(magrittr)
library(tidytext)
library(stringr)
library(viridis)
library(wordcloud)
library(SnowballC)
library(knitr)
```


And the data.
```{r load-data}
load("../data_polit_twitter/tweets_df.Rdata")
load("../data_polit_twitter/tweet_tokens.Rdata")
load("../data_polit_twitter/polits_df.Rdata")
load("data/party_pal.Rdata")
load("../data_polit_twitter/party_pop_scores.Rdata")

```


Run this if some columns are matrices:

```{r}

polits_df %>% 
  mutate_all(funs(c)) -> polits_df

```


# Aspects of the populism measure


- Relative number of exclamation marks '!'
- Relative number of '1 / question marks' '?'
- Positivity score (score of 'Pos - Neg')
- Emotionality score (socre of 'Pos + Neg')
- Ratio of adjectives/adverbs
- ~~Mean number of characters per sentence~~
- Mean number of characters per word
- Relative number of semicolons ';'
- Relative number of words in CAPITAL LETTERS



# Get quotation/exclamation marks per policitian


```{r}
head(tweets_df)

tweets_df %>% 
  select(party, screenName, text) %>% 
  group_by(screenName) %>% 
  summarise(exclamation_marks_abs = str_count(text, pattern = "!") %>% sum,
            exclamation_marks_rel = exclamation_marks_abs / n(),
            party = first(party),
            complement_question_mark_rel = str_count(text, pattern = "\\?") %>% 
              sum %>% `/`(., n())) %>% 
  ungroup -> populism_scores
  
```


## Join with polits df 


```{r eval = FALSE}
populism_scores %>% 
  select(-party)  %>%  # prevent duplicate column
  left_join(polits_df, by = "screenName") %>% 
  mutate(exclamation_prop = exclamation_marks_abs / word_count) -> polits_df
```




## Add relative number of semicolons

```{r}
tweets_df %>% 
  select(party, text, screenName) %>% 
  unnest_tokens(output = token, input = text) %>%  
  dplyr::filter(str_detect(token, ";")) %>% 
  select(-party) %>% 
  group_by(screenName) %>% 
  mutate(semicolon_n = n()) %>% 
  select(-token) %>% 
  full_join(polits_df) -> polits_df
```

I just leave the absolute number of semicolons, because only 1 account used semicolons at all.


# (Relative) number of words in CAPITAL LETTERS



```{r}
names(tweets_df)

tweets_df %>% 
  select(party, text, screenName) %>% 
  mutate(text = str_replace(text, "https*://\\S+", ""),  #remove links
         text = str_replace(text, "#\\S+", ""),  # remove hashtags
         rext = str_replace(text, "RT", ""),  # remove "RT"
         text = str_replace(text, "@\\S+", "")) %>%  # remove mentions
  #mutate(token = str_replace(text, " ", "")) %>% 
  #filter(str_detect(text, "[[:upper:]]{4,}")) %>% 
  mutate(cap_count = str_count(text,  "[[:upper:]]{4,}")) %>% 
  select(-party) %>% 
  group_by(screenName) %>% 
  summarise(cap_count = sum(cap_count, na.rm = T)) %>% 
  full_join(polits_df, by = "screenName") %>%  
  mutate(cap_prop = cap_count / word_count) %>% 
  ungroup -> polits_df


```





# Compute z-scores, and mean/md z-score


## Compute more indicators

```{r comp-indicators}
polits_df %>% 
  mutate(cap_prop = cap_count / word_count,
         neg_prop = neg_words_n / word_count,
         pos_prop = pos_words_n / word_count,
         adj_adv_quote = adjx_n / adv_n) -> polits_df


# polits_df %>% ungroup -> polits_df

```


## Vector of pop scores

```{r}
pop_vars <- c("word_length_md_comp", 
              "emo_score_neg", 
              "emo_abs_score",
              "neg_words_ratio", 
              "cap_prop", 
              "neg_prop", 
              "adj_adv_quote",
              "emo_words_prop")


pop_vars_z <- sapply(pop_vars, function(col) paste0(col, "_z")) %>% as.character


length(pop_vars)

```



## Turn all indicators in right direction

Compute complements `comp` to change direction

```{r check-sign-of-pop-indicators}

polits_df %>% 
  mutate(semicolon_n = NULL,  # remove this variable, nearly all missing
         word_length_md_comp = 1 / word_length_md,
         emo_score_neg = -emo_score,  # flip signs
         emo_abs_score = emo_abs_score,
         neg_prop = neg_prop,
         cap_prop = cap_prop,
         adj_adv_quote = adj_adv_quote,
         emo_words_prop = neg_prop + pos_prop) %>% 
  ungroup -> polits_df
         
```



## Compute z scores of pop indicators

```{r}
polits_df %>% 
  mutate_at(pop_vars, 
            funs(z = as.vector(scale(.)))) -> polits_df
```



## Compute summary populism score


```{r}
polits_df %>% 
  rowwise() %>% 
  mutate(pop_z_md = median(c(word_length_md_comp_z, 
                             emo_score_neg_z, 
                             emo_abs_score_z,
                             neg_words_ratio_z, 
                             cap_prop_z, 
                             neg_prop_z, 
                             adj_adv_quote_z,
                             emo_words_prop_z), na.rm = T)) %>% 
  ungroup -> polits_df
```




## Plot pop scores by party, total score

```{r}
polits_df %>% 
  group_by(party) %>% 
  filter( party != "fraktionslos") %>% 
  summarise(pop_z_md = median(pop_z_md, na.rm = TRUE)) %>% 
  ggplot +
  aes(x = reorder(party, pop_z_md), y = pop_z_md, fill = party) +
  geom_col() +
  coord_flip() +
  labs(x = "Partei",
       y = "Populismuswert",
       fill = "Partei",
       caption = "Median über alle Populismus-Indikatoren") +
  scale_fill_manual(values = party_pal) -> p_party_pop_scores

p_party_pop_scores

ggsave(p_party_pop_scores, file = "img/party_pop_scores.pdf")

```

## Plot individual accounts for each party

```{r}
polits_df %>% 
   group_by(party) %>% 
  filter( party != "fraktionslos") %>% 
  summarise(pop_z_md = median(pop_z_md, na.rm = TRUE)) -> parties_pop_z_md
```


```{r}
polits_df %>% 
  group_by(party, screenName) %>% 
  filter( party != "fraktionslos") %>% 
  summarise(pop_z_md = median(pop_z_md, na.rm = TRUE)) %>% 
  ggplot +
  geom_point(data = parties_pop_z_md, 
             aes(x = reorder(party, pop_z_md), y = pop_z_md), 
             shape = 5, size = 5, color = "grey20") +
  # aes(x = reorder(party, pop_z_md), y = pop_z_md, color = party) +
  geom_jitter(width = .1, aes(x = party, y = pop_z_md, color = party)) +
  coord_flip() +
  labs(x = "Partei",
       y = "Populismuswert",
       color = "Partei",
       caption = "dargestellt sind Mediane über alle Populismus-Indikatoren") +
  scale_color_manual(values = party_pal) -> p_party_pop_scores_individual

p_party_pop_scores_individual

ggsave(p_party_pop_scores_individual, file = "img/p_party_pop_scores_individual.pdf")
ggsave(p_party_pop_scores_individual, file = "img/p_party_pop_scores_individual.png")

```



## Compute pop scores by party, details

```{r comp-party-pop-scores}
polits_df %>% 
  group_by(party) %>% 
  filter(party != "fraktionslos") %>% 
  summarise_at(vars(word_length_md_comp_z, 
                      emo_score_neg_z, 
                      emo_abs_score_z,
                      neg_words_ratio_z, 
                      cap_prop_z, 
                      neg_prop_z, 
                      adj_adv_quote_z,
                      emo_words_prop_z), 
               funs(mean, median), na.rm = T) %>% 
  mutate_all(funs(c)) %>% 
  ungroup -> party_pop_scores
  
```


## Pop row summaries (mean/median)

```{r comp-pop-scores-row-summaries}

# compute row summaries (total pop score)

party_pop_scores %>%   
  rowwise() %>% 
  mutate(pop_score_md = median(c(word_length_md_comp_z_median, 
                             emo_score_neg_z_median, 
                             emo_abs_score_z_median,
                             neg_words_ratio_z_median, 
                             cap_prop_z_median, 
                             neg_prop_z_median, 
                             adj_adv_quote_z_median,
                             emo_words_prop_z_median), na.rm = T),
        pop_score_mean = mean(c(word_length_md_comp_z_median, 
                             emo_score_neg_z_median, 
                             emo_abs_score_z_median,
                             neg_words_ratio_z_median, 
                             cap_prop_z_median, 
                             neg_prop_z_median, 
                             adj_adv_quote_z_median,
                             emo_words_prop_z_median), na.rm = T)) %>% 
    ungroup -> party_pop_scores

party_pop_scores %>% glimpse

```


## Plot again, different score computation (totals)

```{r plot-party-pop-scores}
party_pop_scores %>% 
  ggplot(aes(x = reorder(party, pop_score_md), y = pop_score_md, fill = party)) +
  geom_col() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Partei",
       fill = "Partei",
       y = "Populismuswert",
       caption = "dargestellt sind Mediane aggregiert über Tweets und Accounts") +
  coord_flip() -> p_party_pop_scores_2

p_party_pop_scores_2

ggsave(p_party_pop_scores_2, file = "img/p_party_pop_scores_2.pdf")
```

For comparision, same data, different computation

```{r}
p_party_pop_scores
```

## Pop scores without Trump (per party)

```{r plot-party-pop-scores-without-trump}
party_pop_scores %>% 
  filter(!party %in% c("trump")) %>% 
  ggplot(aes(x = reorder(party, pop_score_md), y = pop_score_md, fill = party)) +
  geom_col() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Partei",
       fill = "Partei",
       y = "Populismuswert",
       caption = "dargestellt sind Mediane aggregiert über Tweets und Accounts") +
  coord_flip() -> p_party_pop_scores_wo_trump

p_party_pop_scores_wo_trump

ggsave(p_party_pop_scores_wo_trump, file = "img/p_party_pop_scores_wo_trump.pdf")
```


## String of pop vars in German

```{r}
pop_vars_de_median <- c(word_length_md_comp_z_median = "Wortkürze",
                 neg_words_ratio_z_median = "Verhältnis negativer/positiver Wörter",
                 neg_prop_z_median = "Anteil negativer Wörter",
                 emo_words_prop_z_median =  "Anteil emotionaler Wörter",
                 emo_score_neg_z_median =  "Wert an negativer Emotion",
                 emo_abs_score_z_median = "Wert an Emotionalität",
                 cap_prop_z_median = "Anteil GROSSBUCHSTABEN",
                 adj_adv_quote_z_median =  "Verhältnis Adjektiven zu Adverben")

pop_vars_de <- c(word_length_md_comp_z = "Wortkürze",
                 neg_words_ratio_z = "Verhältnis negativer/positiver Wörter",
                 neg_prop_z = "Anteil negativer Wörter",
                 emo_words_prop_z =  "Anteil emotionaler Wörter",
                 emo_score_neg_z =  "Wert an negativer Emotion",
                 emo_abs_score_z = "Wert an Emotionalität",
                 cap_prop_z = "Anteil GROSSBUCHSTABEN",
                 adj_adv_quote_z =  "Verhältnis Adjektiven zu Adverben")


```



## Plot populism indicators per party


```{r}
party_pop_scores %>% 
  select(contains("median"), party) %>% 
  gather(key = Indikator, value = z_Wert, -party) %>% 
  ggplot +
  aes(x = Indikator, y = z_Wert, fill = party) +
  geom_col() +
  facet_wrap(~party) +
  scale_fill_manual(values = party_pal) + 
  labs(caption = 
         "dargestellt sind Mediane über alle Tweets aller Politiker") +
  scale_x_discrete(labels = pop_vars_de_median) +
  coord_flip() -> p_party_pop_scores_details

p_party_pop_scores_details

ggsave(p_party_pop_scores_details, 
       file = "img/p_party_pop_scores_details.pdf", 
       width = 7,
       height = 5)

```



## Plot populism indicators per party without Trump


```{r}
party_pop_scores %>% 
  select(contains("median"), party) %>% 
  filter(party != "trump") %>% 
  gather(key = Indikator, value = z_Wert, -party) %>% 
  ggplot +
  aes(x = Indikator, y = z_Wert, fill = party) +
  geom_col() +
  facet_wrap(~party) +
  scale_fill_manual(values = party_pal) + 
  labs(caption = 
         "dargestellt sind Mediane über alle Tweets aller Politiker") +
  scale_x_discrete(labels = pop_vars_de_median) +
  coord_flip() -> p_party_pop_scores_details_no_trump

p_party_pop_scores_details_no_trump

ggsave(p_party_pop_scores_details_no_trump, 
       file = "img/p_party_pop_scores_details_no_trump.pdf", 
       width = 7,
       height = 5)

```



# Plot most populist politicians

```{r}
polits_df %>% 
  filter(!is.na(party)) %>% 
  top_n(10, pop_z_md) %>% 
  ggplot +
  aes(x = reorder(screenName, pop_z_md), y = pop_z_md, fill = party) %>% 
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = party_pal) +
  labs(x = "Name",
       y = "Populismuswert",
       fill = "Partei") -> p_pop_screenName


p_pop_screenName


ggsave(p_pop_screenName,
       file = "img/p_pop_screenName.pdf")

```

### Closer look to Karl_Lauterbach


```{r}
polits_df %>% 
  filter(screenName == "Karl_Lauterbach") %>% 
  select(pop_vars_z) %>% 
  gather(Indikator, Wert) %>% 
  ggplot +
  aes(x = reorder(Indikator, Wert), y = Wert) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = pop_vars_de) +
  labs(x = "Indikator", y = "Z-Wert") -> p_most_pop_screenName


p_most_pop_screenName

ggsave(p_most_pop_screenName,
       file = "img/p_most_pop_screenName.pdf")
```


## Some tweets

```{r}
tweets_df %>% 
  filter(screenName == "Karl_Lauterbach") %>% 
  sample_n(10) %>% 
  pull(text) -> top_1_pop_account_sample_tweets

save(top_1_pop_account_sample_tweets, 
     file = "../data_polit_twitter/top_1_pop_account_sample_tweets.Rdata")
```


# Save data

```{r}
# save(populism_scores, file = "../data_polit_twitter/populism_scores.Rdata")
save(polits_df, file = "../data_polit_twitter/polits_df.Rdata")
save(party_pop_scores, file = "../data_polit_twitter/party_pop_scores.Rdata")
```

