---
title: "Computing a populism measure"
author: "Sebastian Sauer"
date: "3 8 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath('../'))


knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      fig.align = "center",
                      cache = TRUE)
```



Let's perform some initial analyses of polit tweets.

# Setup


First load some libraries.

```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(magrittr)
library(tidytext)
library(stringr)
library(viridis)
library(wordcloud)
library(SnowballC)
library(knitr)
```


And the data.
```{r load-data}
load("../data_polit_twitter/tweets_df.Rdata")
polits_df <- read_csv("../data_polit_twitter/polits_df.csv")
```



# Aspects of the populism measure


- Relative number of exclamation marks '!'
- Relative number of '1 / question marks' '?'
- Positivity score (score of 'Pos - Neg')
- Emotionality score (socre of 'Pos + Neg')
- Ratio of adjectives/adverbs
- ~~Mean number of characters per sentence~~
- Mean number of characters per word
- Relative number of semicolons ';'



# Get quotation/exclamation marks per policitian


```{r}
head(tweets_df)

tweets_df %>% 
  select(party, screenName, text) %>% 
  group_by(screenName) %>% 
  summarise(exclamation_marks_abs = str_count(text, pattern = "!") %>% sum,
            exclamation_marks_rel = exclamation_marks_abs / n(),
            party = first(party),
            complement_question_mark_rel = str_count(text, pattern = "\\?") %>% 
              sum %>% `/`(1, .)) -> populism_scores
  
```

